Concurrent Programming with Harmony

### 2020-08-09 book/paper.tex
New solutions

  description={is a method in execution.  We do not make the distinction

@@

\begin{problems}
\item Harmony programs can usually be easily translated into Python.  For example,
\autoref{fig:incpy} is a Python version of \autoref{fig:inc}.
\begin{enumerate}
\item Run \autoref{fig:incpy} using Python.  Does the assertion fail?
\item Using a script, run \autoref{fig:incpy} 1000 times.
For example, if you are using the bash shell, you can do the following:
\begin{code}
\begin{verbatim}
for i in {1..1000}
do
    python Up.py
done
\end{verbatim}
\end{code}
How many times does the assertion fail (if any)?
\end{enumerate}
\item \autoref{fig:incmany} is a version of \autoref{fig:incpy} that has each
incrementer thread increment \textit{count} \texttt{N} times.  Run \autoref{fig:incpy}
10 times (using Python).
Report how many times the assertion fails and what the value of \textit{count}
was for each of the failed runs.
Also experiment with lower values of \texttt{N}.
How large does \texttt{N} need to be for assertions to fail?
\item Can you think of a fix to \autoref{fig:inc}?  Try one or two different fixes
and run them through Harmony.  Do not worry about having to come up with a correct fix at this
time---the important thing is to develop an understanding of concurrency.
\end{problems}

@@

\section*{Exercises}
\begin{problems}
\item Run \autoref{fig:cs} using Harmony.  As there is no protection of the critical
section, mutual exclusion is violated,
the assertion should fail, and a trace should be reported.
Now plug the following code \textbf{while} \texttt{True}: \textbf{pass};;
just before entering the critical section
in \autoref{fig:cs} and run Harmony again.
Mutual exclusion is guaranteed but progress is violated.
Harmony should print a trace
to a state from which a terminating state cannot be reached.
Describe in English the difference in the failure reports before
and after inserting the code.
\item See if you can come up with some different approaches that satisfy both
mutual exclusion and progress.  Try them with Harmony and see if they work or not.
If they don't, try to understand why.
Do not despair if you can't figure it out---as
we will find out, it is possible but not easy.
\end{problems}

>>>>

  description={is code in execution.  We do not make the distinction

@@

\begin{problems}
\item Harmony programs can usually be easily translated into Python.  For example,
\autoref{fig:incpy} is a Python version of \autoref{fig:inc}.
\begin{enumerate}
\item Run \autoref{fig:incpy} using Python.  Does the assertion fail?
\item Using a script, run \autoref{fig:incpy} 1000 times.
For example, if you are using the bash shell (in Linux, say), you can do the following:
\begin{code}
\begin{verbatim}
for i in {1..1000}
do
    python Up.py
done
\end{verbatim}
\end{code}
How many times does the assertion fail (if any)?
\end{enumerate}
\item \autoref{fig:incmany} is a version of \autoref{fig:incpy} that has each
incrementer thread increment \textit{count} \texttt{N} times.  Run \autoref{fig:incpy}
10 times (using Python).
Report how many times the assertion fails and what the value of \textit{count}
was for each of the failed runs.
Also experiment with lower values of \texttt{N}.
How large does \texttt{N} need to be for assertions to fail?
\item Can you think of a fix to \autoref{fig:inc}?  Try one or two different fixes
and run them through Harmony.  Do not worry about having to come up with a correct fix at this
time---the important thing is to develop an understanding of concurrency.
\end{problems}

@@

\section*{Exercises}
\begin{problems}
\item Run \autoref{fig:cs} using Harmony.  As there is no protection of the critical
section, mutual exclusion is violated,
the assertion should fail, and a trace should be reported.
Now insert the following code:
\begin{code}
\begin{tabbing}
XX\=XXX\=XXX\kill
\textbf{while} \texttt{True}: \\
\> \textbf{pass}; \\
;
\end{tabbing}
\end{code}
just before entering the critical section
in \autoref{fig:cs} and run Harmony again.
Mutual exclusion is guaranteed but progress is violated.
Harmony should print a trace
to a state from which a terminating state cannot be reached.
Describe in English the difference in the failure reports before
and after inserting the code.
\item See if you can come up with some different approaches that satisfy both
mutual exclusion and progress.  Try them with Harmony and see if they work or not.
If they don't, try to understand why.
Do not despair if you can't figure it out---as
we will find out, it is possible but not easy.
\end{problems}
